### 2018-01-04 icde/revision/sec-alg.tex

The core idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.

>>>>

The main idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.
